# Code-a-thon Project Template

This project is intended to help you apply your skills in R in a way that would be conducive for collaborating or creating reproducible analyses.


## Data Used

Identify a dataset to analyze. Remember that if you share the data you must **not violate any privacy restrictions**

If you don't have your own data, options for places to find data are listed on https://daseh.org.

You might start by setting up an R Project, importing your data, previewing the data, etc. 

```{r}
library(tidyverse)
library(naniar)
library(ggplot2)
library(esquisse)

WQ_sites <- read_csv("~/School/DaSEH/DaSEH_Codeathon/WQ_Sites.csv")
head(WQ_sites) #preview data types

colnames(WQ_Samples_sub)

WQ_Samples %>% select(CharacteristicName) %>% unique()
WQ_Samples_sub %>% select(`ResultAnalyticalMethod/MethodIdentifier`) %>% unique()


```

**describe** what your data looks like and **where** you got it. Identify what the variables and samples are, or point to a data dictionary. Describe how the data was originally created. 


# Data Cleaning/Wrangling

Perform any data subsetting, cleaning, or manipulation methods that were described in this course on your data. Examples are: renaming the columns, recoding values, reshaping the data, filtering the data etc. 

You might also research other methods to include here, especially if your data is very unique.

```{r}
WQ_sites <- mutate(WQ_sites, CountyCode = 
                     as.integer(pull(WQ_sites, CountyCode))) #CountyCodes to integers

WA_counties <- WA_counties %>% 
  mutate(County = str_remove(County, " County, WA")) %>% 
  mutate(CountyCode = sequence(i = 1, nvec = 39 , by = 2)) #creates col to associate counties with numeric code
head(WA_counties)

WQ_sites %>% mutate(County = )

WQ_Samples_sub <- WQ_Samples %>% 
  filter(ActivityMediaName == "Water" &
           !str_detect(ActivityTypeCode, "Control") &
           str_detect(OrganizationFormalName, "Trib") & 
           ResultSampleFractionText != "Dissolved" & 
           ResultStatusIdentifier == "Final" & 
           (str_detect(`ResultAnalyticalMethod/MethodIdentifier`,"6010")|
              str_detect(`ResultAnalyticalMethod/MethodIdentifier`,"6020")| 
              str_detect(`ResultAnalyticalMethod/MethodIdentifier`,"7010")| 
              str_detect(`ResultAnalyticalMethod/MethodIdentifier`,"200.7")| 
              str_detect(`ResultAnalyticalMethod/MethodIdentifier`,"200.8")|
              str_detect(`ResultAnalyticalMethod/MethodIdentifier`,"200.9")|
              str_detect(`ResultAnalyticalMethod/MethodIdentifier`,"7470")
            )
         ) 
WQ_Samples_sub <- WQ_Samples_sub %>%
  drop_na(ResultSampleFractionText) 
#filter for accepted tribal water total metals data w/o QC samples

WQ_Samples_sub <- WQ_Samples_sub %>% select(OrganizationFormalName, ActivityStartDate, ProjectName, MonitoringLocationName, `ActivityLocation/LatitudeMeasure`, `ActivityLocation/LongitudeMeasure`, ResultIdentifier, CharacteristicName, ResultMeasureValue, `ResultMeasure/MeasureUnitCode`, `ResultAnalyticalMethod/MethodIdentifier`)
#select relevant columns

WQ_Samples_sub <- WQ_Samples_sub %>%
  filter(
    CharacteristicName %in% c("Arsenic", "Cadmium", "Chromium", "Copper", "Lead", "Mercury", "Zinc" )
  ) #filter for contaminant metals

WQ_Samples_sub <- WQ_Samples_sub %>%
  rename(Latitude = `ActivityLocation/LatitudeMeasure`, 
         Logitude = `ActivityLocation/LongitudeMeasure`,
         ResultMeasureUnit = `ResultMeasure/MeasureUnitCode`,
         AnalyticalMethod = `ResultAnalyticalMethod/MethodIdentifier`)

WQ_Samples_sub <- WQ_Samples_sub %>%
  drop_na(ResultMeasureValue)
#remove missing results

WQ_Samples_sub <- WQ_Samples_sub %>%
  mutate(
    ResultMeasureValue = case_when(
             str_detect(ResultMeasureValue, '<') ~ '0',
         TRUE ~ ResultMeasureValue
         )
  ) #convert n.d. to zeros

WQ_Samples_sub <- WQ_Samples_sub %>%
  mutate(
    ResultMeasureValue = str_remove(ResultMeasureValue, ",")
  ) %>%
  mutate(
    ResultMeasureValue_ppb = as.numeric(ResultMeasureValue)
    ) %>%
  mutate(
    ResultMeasureValue_ppb = case_when(
      ResultMeasureUnit == "mg/L" ~ ResultMeasureValue_ppb*1000,
    TRUE ~ ResultMeasureValue_ppb
    )
  ) #create numeric column with standardized units

WQ_Samples_sub <- WQ_Samples_sub %>%
  mutate(
    ActivityStartYear = 
      str_sub(ActivityStartDate, start = 1, end = 4) ) %>%
  filter(ActivityStartYear >= 2000)%>%  
  group_by(
    across(c(ActivityStartYear, CharacteristicName)) ) %>%
  mutate(
    AverageYearlyLvl = mean(ResultMeasureValue_ppb)
  ) #create year column and avg column by year and analyte
```


# Data Visualization

Create some visualizations of your data using the esquisse app or the ggplot2 package.

```{r}
WQ_Samples_sub %>% filter(CharacteristicName == "Arsenic") %>% ggplot(
  aes(x = ActivityStartYear, y = AverageYearlyLvl, color = CharacteristicName)) +
  geom_line() + facet_wrap(~ CharacteristicName, ncol = 3) +
  theme(legend.position = "none")

esquisser(WA_Samples_sub)
```


# Data Analysis

Perform a **simple analysis** of your data. This can involve summarizing the data to describe aspects about it (quartiles, means, range etc.) or a simple statistical test. 

Don't forget to describe what analysis you performed and why. Provide some simple **interpretation** about what your analysis might indicate about your data.

```{r}

```


# Please include additional sections as desired.

```{r}

```


# Versions

Include some information about the version of R and the packages you are using by running sessionInfo().

```{r}
sessionInfo()
```

Render your document to an html or pdf using the "Knit" button.
