# Code-a-thon Project Template

This project is intended to help you apply your skills in R in a way that would be conducive for collaborating or creating reproducible analyses.


## Data Used

Identify a dataset to analyze. Remember that if you share the data you must **not violate any privacy restrictions**

If you don't have your own data, options for places to find data are listed on https://daseh.org.

You might start by setting up an R Project, importing your data, previewing the data, etc. 

```{r}
library(tidyverse)

WQ_sites <- read_csv("~/School/DaSEH/DaSEH_Codeathon/WQ_Sites.csv")
head(WQ_sites) #preview data types

colnames(WQ_Samples_sub)

WQ_Samples_sub %>% select(CharacteristicName) %>% unique()
WQ_Samples_sub %>% select(`ResultAnalyticalMethod/MethodIdentifier`) %>% unique()

WQ_Samples_sub %>% select(OrganizationFormalName, )
```

**describe** what your data looks like and **where** you got it. Identify what the variables and samples are, or point to a data dictionary. Describe how the data was originally created. 


# Data Cleaning/Wrangling

Perform any data subsetting, cleaning, or manipulation methods that were described in this course on your data. Examples are: renaming the columns, recoding values, reshaping the data, filtering the data etc. 

You might also research other methods to include here, especially if your data is very unique.

```{r}
WQ_sites <- mutate(WQ_sites, CountyCode = 
                     as.integer(pull(WQ_sites, CountyCode))) #CountyCodes to integers

WA_counties <- WA_counties %>% 
  mutate(County = str_remove(County, " County, WA")) %>% 
  mutate(CountyCode = sequence(i = 1, nvec = 39 , by = 2)) #creates col to associate counties with numeric code
head(WA_counties)

WQ_sites %>% mutate(County = )

WQ_Samples_sub <- WQ_Samples %>% filter(ActivityMediaName == "Water" &                                !str_detect(ActivityTypeCode, "Control") & str_detect(OrganizationFormalName, "Trib") &                    (str_detect(`ResultAnalyticalMethod/MethodIdentifier`,"6010")| str_detect(`ResultAnalyticalMethod/MethodIdentifier`,"6020")| str_detect(`ResultAnalyticalMethod/MethodIdentifier`,"7010")| str_detect(`ResultAnalyticalMethod/MethodIdentifier`,"200.7")| str_detect(`ResultAnalyticalMethod/MethodIdentifier`,"200.8"))) #filter for tribal water metal data w/o QC samples


```


# Data Visualization

Create some visualizations of your data using the esquisse app or the ggplot2 package.

```{r}

```


# Data Analysis

Perform a **simple analysis** of your data. This can involve summarizing the data to describe aspects about it (quartiles, means, range etc.) or a simple statistical test. 

Don't forget to describe what analysis you performed and why. Provide some simple **interpretation** about what your analysis might indicate about your data.

```{r}

```


# Please include additional sections as desired.

```{r}

```


# Versions

Include some information about the version of R and the packages you are using by running sessionInfo().

```{r}
sessionInfo()
```

Render your document to an html or pdf using the "Knit" button.
